\setcounter{section}{0}
\section{Introduction}\label{sec:intro}


\vspace{3cm}
\par

\input{Chapters/Introduction/Life_is}
\input{Chapters/Introduction/Molecular_structure}
\input{Chapters/Introduction/Computation}


\subsection{Objectives}
\begin{itemize}
    \item The main objective of this work, is to calculate the free energy of solvation (non-polar) of 20 peptides using classical Molecular Dynamics Simulation method.
    \item Compare the results of the explicit MD model with the calculations given by the implicit solvent models available by measure the accuracy of them.
    \item  Become familiar with the use of GROMOS++ software for the calculation of free energies using Thermodynamic Integration. 
    \item Study the behavior of the van der Waals interaction and its contribution to the solvation process. 
    \item Simulate 20 alanine-peptides in a pre-equilibrated water box to preform the free energy calculations. 
\end{itemize}

This document is organized as follow: Section \ref{sec:MD}, presents an overview of the Molecular Dynamics (MD) method, which is the tool to preform the calculations of the free energies of solvation described in the abstract and the criteria and requirements needed to build this method. It also provides a characterization of the force-fields whit a special attention to describe the nature of non-bonded interaction which is the main subject treated in this work.
In Section \ref{sec:implicit}, implicit solvent models are explain with they advantages and disadvantages and also the reasons to use this methods as an alternative to MD. In particular, Section \ref{subsec:CC_method} described a novel way to calculate $\Delta G_{solv}$, sharing the same ideas as the implicit solvent models, but with a clearer physical meaning than current available models. 
Next, Section \ref{sec:Free_energy} presents the underlying thermodynamic and statistical mechanics theory that had been develop to calculate free energies, with the mathematical construction of these models. Section \ref{sec:methods} talks about the methodology used to compute the free energy results, starting with the preparation of the molecular structures (Section \ref{subsec:strucutre_prep}), following by a review of the scope and functionality of GROMOS simulation software, explaining how it was used to preform such calculations step by step. 
Finally, in Section \ref{sec:results} the results and comparison between the models explained above are presented.

